\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/appendix.tex
prepare addition of scaling analysis

>>>>

\subsection{Influence of scale}
To obtain first insights in how the performance \glspl{llm} depends on scale, we tested the \glspl{llm} of the LLaMA series. 
Note that such analyses are difficult as models are typically not directly comparable in terms of dataset and training protocol.\autocite{biderman2023pythia}

\Cref{fig:llama_performance} shows the performance of the LLaMA (chat) models with different parameter counts on the \chembench corpus.

\begin{figure}
    \centering 
    \includegraphics{figures/llama_performance.pdf}
    \caption{\textbf{Performance of LLaMA models on the \chembench corpus.} The plot shows the fraction of correctly answered questions as a function of the model size.}
    \label{fig:llama_performance}
    \script{analyze_llama_performance.py}
\end{figure}
